Inferring Graphics Programs from Images

### 2017-05-03 paper.tex
pseudocode for SMC

@@

>>>>

\section{Introducing visual programs}

In this work we consider programs that draw diagrams, similar to those found in papers.

@@

  \begin{algorithm}[tb]
   \caption{Neurally guided SMC}
   \label{guideAlgorithm}
\begin{algorithmic}
  \STATE {\bfseries Input:} Neural network NN, beam size $N$, maximum length $L$, target image $x$
  \STATE {\bfseries Output:} Samples of the program trace
  \STATE Set $B_0 = \{\text{empty program}\}$
  \FOR{$1\leq l\leq L$}
  \FOR{$1\leq n\leq N$}
  \STATE{ $p_n\sim \text{Uniform}(B_{l - 1})$}
  \STATE{ $p'_{n}\sim \text{NN}(\text{render}(p),x)$}
  \STATE{ Define $r_n = p'_n\cdot p_n$}
  \STATE{ Set $\tilde{w}(r_n) = \frac{L(x|r_n)}{L(x|p_n)}\times\frac{\probability [p'_n]}{\probability [p'_n = \text{NN}(\text{render}(p),x)]}$}
  \ENDFOR
  \STATE{ Define $w(p) = \frac{\tilde{w}(p)}{\sum_{p'}\tilde{w}(p')}$}
  \STATE{ Set $B_l$ to be $N$ samples from $r_n$ distributed according to $w(\cdot)$}
  \ENDFOR
  \STATE {\bfseries return} $\{p : p\in B_{l\leq L}, p \text{ is finished}\}$
\end{algorithmic}
  \end{algorithm}
